Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-17 arxiv/proof_examples.tex
appendix

We follow a similar logic from Theorem \ref{thm_many_tasks}.
We characterize the global minimizer of $f(A, B)$ in the random-effects model.

@@

Using the local optimality condition $\frac{\partial f}{\partial B} = 0$, we have that $\hat{B}$ satisfies the following

@@

		\hat{B} \define  (A_1^2 (X^{(1)})^{\top}X^{(1)} + A_2^2 (X^{(2)})^{\top}X^{(2)})^{-1} (A_1 (X^{(1))})^{\top}Y^{(1)} + A_2 (X^{(2)})^{\top}Y^{(2)}). \label{eq_Bhat_2task} %\\

@@

		 g(x) \define & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1)+ \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} \right. \nonumber\\

@@

		 + & \left\| X^{(2)} \hat \Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (x\beta_1-x^2\beta_2)+ \left(X^{(2)}\hat\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2}\right)\epsilon^{(2)} \right. \nonumber\\

@@

The conditional expectation of $g(x)$ over $\epsilon_1$ and $\epsilon_2$ is

@@

\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta_1,\beta_2}
&= \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)\right\|^2 \nonumber\\
&+x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-x\beta_2)\right\|^2  \nonumber\\
& + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}} \nonumber\\
&+\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\hat \Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2\epsilon^{(2)}}   \nonumber\\

@@

 & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)\right\|^2  +x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-x\beta_2)\right\|^2 \\
=&(\beta_1-x\beta_2)^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)}  (\beta_1-x\beta_2)\\
&+(\beta_1-x\beta_2)^\top x^2 (X^{(1)})^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)} )^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-x\beta_2)\\
%&=(\beta_1-x\beta_2)^\top\left[ x^2 (X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}  \right]\hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)\\
=&(\beta_1-x\beta_2)^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2).

@@

		&\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta_1,\beta_2} \\
		=& (\beta_1-x\beta_2)^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)  \\
		&+ \sigma^2\tr\left[ \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2+ \left(X^{(2)}\hat\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2 \right]\\

@@

		=& (\beta_1-x\beta_2)^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2) +\sigma^2(n_1+n_2-p).

@@

For the random-effects model, recall that the entries of $\beta_1, \beta_2\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variance $\kappa^2/p, d^2/p$, respectively.

@@

&\exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(x) \mid X_1, X_2} \nonumber\\

@@

&=\frac{(x-1)^2\kappa^2 + (x^2+1)d^2/2}{p} \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p), \label{EgA}

@@

First, we show that $g(x)$ and $\ex{g(x) \mid X^{(1)}, X^{(2)}}$ are close using standard concentration bounds.
\begin{claim}\label{claim_largedev1}
 In the setting of Corollary \ref{cor_MTL_loss}, we have that with high probability
$$\left| g(x) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(x) \mid X_1, X_2 }\right| \le p^{1/2+c} \left(\sigma^2 + \kappa^2+d^2 \right).$$
%for any small constant $c>0$.
 \end{claim}
 \begin{proof}
By Fact \ref{fact_minv}(ii), we have that with high probability,
 \be\label{op_X12}
\|X^{(1)}\|\le \sqrt{(\sqrt{n_1} + \sqrt{p})^2 + n_1 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p}, \quad \|X^{(2)}\|\le \sqrt{(\sqrt{n_2} + \sqrt{p})^2 + n_2 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p},
 \ee
 and
 \be\label{op_Sig1}
\| \hat\Sigma(x)^{-1}\|\le \frac1{x^2[(\sqrt{n_1} - \sqrt{p})^2 - n_1 \cdot p^{-c_{\varphi}}]+[(\sqrt{n_2} - \sqrt{p})^2 - n_2 \cdot p^{-c_{\varphi}}] }\lesssim \frac{1}{(x^2+1)p},
 \ee
where we used that $1+\tau\le \rho_1=n_1/p\le \tau^{-1}$ and $1+\tau\le \rho_2=n_2/p\le \tau^{-1}$ for a small constant $\tau>0$.

 Now we expand the first term on the right-hand side of \eqref{eq_mtl_A12}:
 \begin{align}
 & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1)+ \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} \right. \nonumber\\
		& \left. + x X^{(1)}\hat \Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2=h_1(x) + h_2(x) +h_3(x) + 2h_4(x) + 2h_5(x) + 2h_6(x) ,\label{expand_6}
 \end{align}
 where
 \begin{align*}
&h_1(x):=  (\beta_1-x\beta_2)^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)  ,\\
& h_2(x) := {(\epsilon^{(1)})^\top \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}}  ,\\
& h_3(x):=  x^2 { (\epsilon^{(2)} )^\top X^{(2)} \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)}} , \\
& h_4(x):=  (\epsilon^{(1)})^\top\left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1), \\
&h_5(x):=x (\epsilon^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1),\\
&h_6(x):=x (\epsilon^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)}.
\end{align*}
Next we estimate each term using Lemma \ref{largedeviation} in Appendix \ref{app_tool}.

For $h_1(x)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that the entries of $\beta_1-x\beta_2\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variance $p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]$, we obtain the following estimate with high probability for any small constant $c>0$:
\begin{align}
&\left|h_1(x) - \exarg{\beta_1,\beta_2}{h_1(x) \mid X_1, X_2}\right|\nonumber \\
&\le p^{c}\cdot p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]\cdot \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F \nonumber\\
&\le p^{c}\cdot p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]\cdot p^{1/2} \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| \nonumber \\
&\lesssim p^{1/2+c}\cdot \frac{(x-1)^2\kappa^2 + (x^2+1)d^2/2}{(x^2+1)^2}\lesssim p^{1/2+c}(\kappa^2 + d^2).\label{eq_hA1}
\end{align}
 Here in the third step we used \eqref{op_X12} and \eqref{op_Sig1} to bound the operator norm:
\begin{align*}
 \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| & \le \left\| (X^{(2)})^\top X^{(2)}\right\|^2 \cdot \left\| (X^{(1)})^\top X^{(1)}\right\|\cdot \left\| \hat\Sigma(x)^{-1} \right\|^2 \\
 & \lesssim \frac{p}{(x^2+1)^2}.
\end{align*}
Similarly, using Lemma \ref{largedeviation}, the fact that the entries of $\epsilon^{(1)},\epsilon^{(2)}\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variances $\sigma^2$, and bounds \eqref{op_X12}-\eqref{op_Sig1}, we can obtain that with high probability,
\be\label{eq_hA23}\left|h_2(x) - \exarg{\epsilon^{(1)}}{h_2(x) \mid X_1, X_2}\right| \lesssim p^{1/2+c}\sigma^2, \quad \left|h_3(x) - \exarg{\epsilon^{(2)}}{h_3(x) \mid X_1, X_2}\right| \lesssim p^{1/2+c}\sigma^2.\ee
For $h_4(x)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool}, we obtain the following estimate with high probability for any small constant $ c>0$:
\begin{align}
&\left|h_4(x)\right| \nonumber\\
&\le p^{c}\cdot \sigma \sqrt{p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]}\cdot \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F\nonumber \\
&\le p^{c}\cdot \sigma \sqrt{p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]} \cdot p^{1/2} \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
&\lesssim p^{c}\cdot \sigma \sqrt{ (x-1)^2\kappa^2 + (x^2+1)d^2/2} \cdot \left\|  \id_{n_1}-x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\right\|  \left\|X^{(1)}\right\| \left\|\hat\Sigma(x)^{-1}\right\|\left\| (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
&\lesssim p^{1/2+c}\frac{\sigma \sqrt{ (x-1)^2\kappa^2 + (x^2+1)d^2/2}}{x^2+1} \lesssim p^{1/2+c}(\sigma^2 + \kappa^2 + d^2),\label{eq_hA4}
\end{align}
where in the fourth step we used $\left\|  \id_{n_1}-x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\right\|\le 1$ and \eqref{op_X12}-\eqref{op_Sig1}, and in the last step we used AM-GM inequality. With same argument, we can show that
\be\label{eq_hA56} \left|h_5(x)\right| \le p^{1/2+c}(\sigma^2 + \kappa^2 + d^2), \quad \left|h_6(x)\right| \le p^{1/2+c}\sigma^2,\ee
with high probability for any small constant $c>0$. %Combining \eqref{eq_hA1}, \eqref{eq_hA23}, \eqref{eq_hA4} and \eqref{eq_hA56}, we conclude that

@@

Next, we show that $\hat x$ is close to 1.
\begin{claim}\label{lem_hat_v}
%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
 In the setting of Corollary \ref{cor_MTL_loss}, we have that with high probability,
%There exists a constant $C>0$ such that
	\be\label{hatw_add1}|\hat x -1|\le  \frac{2d^2}{\kappa^2} + p^{-1/4+c}.
	\ee
%	for any small constant $c>0$.
	%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
\end{claim}

>>>>

We follow a similar logic as in the proof of Theorem \ref{thm_many_tasks}.
We first characterize the global minimizer of $f(A, B)$ in the random-effects model.

@@

Using the local optimality condition $\frac{\partial f}{\partial B} = 0$, we obtain that $\hat{B}$ satisfies the following

@@

		\hat{B} \define  \left[A_1^2 (X^{(1)})^{\top}X^{(1)} + A_2^2 (X^{(2)})^{\top}X^{(2)}\right]^{-1} \left[A_1 (X^{(1))})^{\top}Y^{(1)} + A_2 (X^{(2)})^{\top}Y^{(2)}\right]. \label{eq_Bhat_2task} %\\

@@

		 g(x) \define & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta^{(2)}-\beta^{(1)})+ \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)\epsilon^{(1)} \right. \nonumber\\

@@

		 + & \left\| X^{(2)} \hat \Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (x\beta^{(1)}-x^2\beta^{(2)})+ \left(X^{(2)}\hat\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)\epsilon^{(2)} \right. \nonumber\\

@@

The conditional expectation of $g(x)$ over $\epsilon^{(1)}$ and $\epsilon^{(2)}$ is

@@

\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta^{(1)},\beta^{(2)}}
&= \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})\right\|^2 \nonumber\\
&+x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta^{(1)}-x\beta^{(2)})\right\|^2  \nonumber\\
& + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)^2\epsilon^{(1)}} \nonumber\\
&+\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\hat \Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)^2\epsilon^{(2)}}   \nonumber\\

@@

 & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})\right\|^2  +x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta^{(1)}-x\beta^{(2)})\right\|^2 \\
=&(\beta^{(1)}-x\beta^{(2)})^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)}  (\beta^{(1)}-x\beta^{(2)})\\
&+(\beta^{(1)}-x\beta^{(2)})^\top x^2 (X^{(1)})^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)} )^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta^{(1)}-x\beta^{(2)})\\
%&=(\beta^{(1)}-x\beta^{(2)})^\top\left[ x^2 (X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}  \right]\hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})\\
=&(\beta^{(1)}-x\beta^{(2)})^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)}).

@@

		&\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta^{(1)},\beta^{(2)}} \\
		=& (\beta^{(1)}-x\beta^{(2)})^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})  \\
		&+ \sigma^2\tr\left[ \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)^2+ \left(X^{(2)}\hat\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)^2 \right]\\

@@

		=& (\beta^{(1)}-x\beta^{(2)})^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)}) +\sigma^2(n_1+n_2-p).

@@

For the random-effects model, recall that the entries of $(\beta^{(1)}- x\beta^{(2)})\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variance $p^{-1}[(x-1)^2\kappa^2 +(1+x^2) d^2]$.

@@

&\exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta^{(1)},\beta^{(2)}}{g(x) \mid X_1, X_2} \nonumber\\

@@

&=\frac{(x-1)^2\kappa^2 + (x^2+1)d^2}{p} \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p), \label{EgA}

@@

First, we show that $g(x)$ and $\ex{g(x) \mid X^{(1)}, X^{(2)}}$ are close using standard concentration bounds.
\begin{claim}\label{claim_largedev1}
 In the setting of Corollary \ref{cor_MTL_loss}, we have that with high probability
$$\left| g(x) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta^{(1)},\beta^{(2)}}{g(x) \mid X_1, X_2 }\right| \le p^{1/2+c} \left(\sigma^2 + \kappa^2+d^2 \right)$$
for any small constant $c>0$.
 \end{claim}
 \begin{proof}
By Fact \ref{fact_minv} (ii), we have that with high probability,
 \be\label{op_X12}
\|X^{(1)}\|\le \sqrt{(\sqrt{n_1} + \sqrt{p})^2 + n_1 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p}, \quad \|X^{(2)}\|\le \sqrt{(\sqrt{n_2} + \sqrt{p})^2 + n_2 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p},
 \ee
 and
 \be\label{op_Sig1}
\| \hat\Sigma(x)^{-1}\|\le \frac1{x^2[(\sqrt{n_1} - \sqrt{p})^2 - n_1 \cdot p^{-c_{\varphi}}]+[(\sqrt{n_2} - \sqrt{p})^2 - n_2 \cdot p^{-c_{\varphi}}] }\lesssim \frac{1}{(x^2+1)p},
 \ee
where we used that $3\le n_1/p\le \tau^{-1}$ and $3\le n_2/p\le \tau^{-1}$ for a small constant $\tau>0$.

 Now we expand the first term on the right-hand side of \eqref{eq_mtl_A12}:
 \begin{align}
 & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta^{(2)}-\beta^{(1)})+ \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)\epsilon^{(1)} \right. \nonumber\\
		& \left. + x X^{(1)}\hat \Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2=h_1(x) + h_2(x) +h_3(x) + 2h_4(x) + 2h_5(x) + 2h_6(x) ,\label{expand_6}
 \end{align}
 where
 \begin{align*}
&h_1(x):=  (\beta^{(1)}-x\beta^{(2)})^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})  ,\\
& h_2(x) := {(\epsilon^{(1)})^\top \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)^2\epsilon^{(1)}}  ,\\
& h_3(x):=  x^2 { (\epsilon^{(2)} )^\top X^{(2)} \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)}} , \\
& h_4(x):=  (\epsilon^{(1)})^\top\left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta^{(2)}-\beta^{(1)}), \\
&h_5(x):=x (\epsilon^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta^{(2)}-\beta^{(1)}),\\
&h_6(x):=x (\epsilon^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)\epsilon^{(1)}.
\end{align*}
Next we estimate each term using Lemma \ref{largedeviation} in Appendix \ref{app_tool}.

For $h_1(x)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that the entries of $(\beta^{(1)}-x\beta^{(2)})\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variance $p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2]$, we obtain the following estimate with high probability for any small constant $c>0$:
\begin{align}
&\left|h_1(x) - \exarg{\beta^{(1)},\beta^{(2)}}{h_1(x) \mid X_1, X_2}\right|\nonumber \\
&\le p^{c}\cdot p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2]\cdot \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F \nonumber\\
&\le p^{c}\cdot p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2]\cdot p^{1/2} \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| \nonumber \\
&\lesssim p^{1/2+c}\cdot \frac{(x-1)^2\kappa^2 + (x^2+1)d^2}{(x^2+1)^2}\lesssim p^{1/2+c}(\kappa^2 + d^2).\label{eq_hA1}
\end{align}
 Here in the third step we used \eqref{op_X12} and \eqref{op_Sig1} to bound the operator norm:
\begin{align*}
 \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| & \le \left\| (X^{(2)})^\top X^{(2)}\right\|^2 \cdot \left\| (X^{(1)})^\top X^{(1)}\right\|\cdot \left\| \hat\Sigma(x)^{-1} \right\|^2 \\
 & \lesssim \frac{p}{(x^2+1)^2}.
\end{align*}
Similarly, using Lemma \ref{largedeviation}, the fact that the entries of $\epsilon^{(1)},\epsilon^{(2)}\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variances $\sigma^2$, and the bounds \eqref{op_X12}-\eqref{op_Sig1}, we can obtain that with high probability,
\be\label{eq_hA23}\left|h_2(x) - \exarg{\epsilon^{(1)}}{h_2(x) \mid X_1, X_2}\right| \lesssim p^{1/2+c}\sigma^2, \quad \left|h_3(x) - \exarg{\epsilon^{(2)}}{h_3(x) \mid X_1, X_2}\right| \lesssim p^{1/2+c}\sigma^2.\ee
For $h_4(x)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool}, we obtain the following estimate with high probability for any small constant $ c>0$:
\begin{align}
&\left|h_4(x)\right| \nonumber\\
&\le p^{c}\cdot \sigma \sqrt{p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2]}\cdot \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F\nonumber \\
&\le p^{c}\cdot \sigma \sqrt{p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2]} \cdot p^{1/2} \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
&\le  p^{c}\cdot \sigma \sqrt{ (x-1)^2\kappa^2 + (x^2+1)d^2} \cdot \left\|  \id_{n_1\times n_1}-x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\right\|  \left\|X^{(1)}\right\| \left\|\hat\Sigma(x)^{-1}\right\|\left\| (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
&\lesssim p^{1/2+c}\frac{\sigma \sqrt{ (x-1)^2\kappa^2 + (x^2+1)d^2}}{x^2+1} \lesssim p^{1/2+c}(\sigma^2 + \kappa^2 + d^2).\label{eq_hA4}
\end{align}
Above, in the fourth step we used $\left\|  \id_{n_1}-x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\right\|\le 1$ and equations \eqref{op_X12} and \eqref{op_Sig1}. In the last step we used AM-GM inequality. With the same argument, we can show that
\be\label{eq_hA56} \left|h_5(x)\right| \le p^{1/2+c}(\sigma^2 + \kappa^2 + d^2), \quad \left|h_6(x)\right| \le p^{1/2+c}\sigma^2,\ee
with high probability for any small constant $c>0$. %Combining \eqref{eq_hA1}, \eqref{eq_hA23}, \eqref{eq_hA4} and \eqref{eq_hA56}, we conclude that

@@

Next, we show that $\hat x$ is close to 1.
\begin{claim}\label{lem_hat_v}
%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
 In the setting of Corollary \ref{cor_MTL_loss}, we have that with high probability,
%There exists a constant $C>0$ such that
	\be\label{hatw_add1}|\hat x -1|\le  \frac{2d^2}{\kappa^2} + p^{-1/4+c}
	\ee
	for any small constant $c>0$.
	%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
\end{claim}

\begin{proof}
Corresponding to equation \eqref{EgA}, we define the function
\begin{align*}
h(x):= [(x-1)^2\kappa^2 + (x^2+1)d^2] \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}\right].
\end{align*}
Using Fact \ref{fact_minv} (ii), we can obtain that with high probability,
\begin{align}
p(x^2+1)^{-1}&\lesssim \left( x^2 \left[(\sqrt{n_2}-\sqrt{p})^{2}-n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}-\sqrt{p})^{2}-n_1p^{-c_\varphi}\right]^{-1} \right)^{-1} \nonumber\\
&\preceq (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} =\left( x^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} \nonumber\\
&\preceq \left( x^2 \left[(\sqrt{n_2}+\sqrt{p})^{2}+n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}+\sqrt{p})^{2}+n_1p^{-c_\varphi}\right]^{-1} \right)^{-1}\lesssim p(x^2+1)^{-1}, \label{op_uplow}
\end{align}
where we also used that $3\le n_1/p \le \tau^{-1}$ and $3\le  n_2/p \le \tau^{-1}$ for a small constant $\tau>0$. Then we get that
\be\label{eq_h1}h(1)= 2d^2 \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat\Sigma(1)^{-1}(X^{(2)})^\top X^{(2)}\right]\lesssim pd^2 .\ee
On the other hand, if $|x-1|\ge \delta$ for a small constant $\delta>0$, then we have
\begin{align}\label{eq_hA}
h(x)\gtrsim (1+x^2)\kappa^2 \cdot p\left( x^2 +1\right)^{-1} =p\kappa^2 ,
\end{align}
where in the first step we used that $|x-1|^2\gtrsim 1+x^2$ for $|x-1|\ge \delta$ and equation \eqref{op_uplow}.
%and in the second step we used equation \eqref{choiceofpara0} \HZ{I'm not sure which condition we use? put it here}.
Hence using Claim \ref{claim_largedev1} and equations \eqref{eq_h1} and \eqref{eq_hA}, we obtain that with high probability,
\begin{align}
g(x)&\ge  h(x) +\sigma^2(n_1+n_2-p) -p^{-1/2+c}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \nonumber\\
&\ge h(1) +\sigma^2(n_1+n_2-p) + p^{-1/2+c}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \ge g(1), \label{gA>g1}
\end{align}
under conditions $\sigma^2 =\OO( \kappa^2)$ and $d^2 =\oo({\kappa^2})$. %\eqref{choiceofpara0} \HZ{again, I don't see which condition we use here?}.
This gives that
%\be\label{rough A-1}
$|\hat x-1|\le \delta$ for any small constant $\delta>0$.
